### 2020-01-06 msc-thesis/chapter/related_work.tex
added msc-thesis

%\documentclass[final,5p,times,twocolumn]{elsarticle}
\documentclass[smallextended]{svjour3}
%\biboptions{numbers,sort&compress}
%\documentclass[sigconf,review, anonymous]{acmart}
%\hyphenation{on-tol-o-gy ad-di-tion-al in-fra-struc-ture an-a-lyze a-nal-y-sis} 
%\input{packages}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Comment the \draftmodetrue line before submission
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifdraftmode
\draftmodetrue

%% avoid footnotes across pages
\interfootnotelinepenalty=10000
%\raggedbottom

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Uncomment \showsplattexttrue to show text from our splat paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifshowsplattext
%\showsplattexttrue

\pagenumbering{arabic}

%% paragraphs within margins
\usepackage[english]{babel}
\setlength{\emergencystretch}{2pt}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
\usepackage{listings}
\usepackage[caption=false, font=footnotesize]{subfig}
%%%%%%%%%%%%% code listing
\renewcommand{\ttdefault}{pcr}
\lstset{
  basicstyle=\scriptsize\ttfamily,
  keywordstyle=\scriptsize\ttfamily\bfseries,
  language=Java,             % choose the language of the code
  frame=single,              % adds a frame around the code
  aboveskip=0pt,
  belowskip=0pt,
  breaklines=true,           % sets automatic line breaking
  breakatwhitespace=false,   % sets if automatic breaks should only happen at
  showspaces=false,
  %numbersep=5pt,              % Abstand der Nummern zum Text
  %tabsize=2,                  % Groesse von Tabs
  %extendedchars=true,         %
  %breaklines=true,            % Zeilen werden Umgebrochen
  keywords=[2]{class, incorporateUserFeedback, testPushPop, testPopPush},
}
\usepackage{balance}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{url}

\input{macros}

\journalname{Software Quality Journal}

\begin{document}

\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
%\titlerunning{Leveraging Diversity to Find Bugs in JavaScript Engines}        % if too long for running head

\author{Igor Lima \and Breno Miranda\footnotemark \and Marcelo d'Amorim}
%\authorrunning{Short form of author list} % if too long for running head

\institute{
* Corresponding author: Breno Miranda \and \email{bafm@cin.ufpe.br}\\ \\
Igor Lima \and \email{isol2@cin.ufpe.br} \\
Breno Miranda \and \email{bafm@cin.ufpe.br} \\
Marcelo d'Amorim \and \email{damorim@cin.ufpe.br} \\
\at Universidade Federal de Pernambuco, Recife, PE, Brazil}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

%\institute{Corresponding author.}

%\renewcommand{\shortauthors}{Lima et al.}

\maketitle

\begin{abstract}
  \input{abstract}
  \keywords{Diversity \and Test Transplantation \and Differential Testing \and JavaScript}
\end{abstract}

\section{Introduction}

JavaScript (\js{}) is one of the most popular programming languages
today~\cite{stackify,redmonk-javascript}, with penetration in various software development segments including, web, mobile,
and, more recently, the Internet of
Things~(IoT)~\cite{simply-technologies}. The interest of the community
for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
lead to sensible changes in engine implementations~\cite{kangax}. Even small
changes can have high practical impact. For example, in October 2014 a
new attribute added to Array objects resulted in the MS Outlook
Calendar web app, which is built in \js{}, to fail under 
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those bugs. It is also
challenging.  Specifications are intentionally incomplete as to enable
development flexibility. In addition, they evolve frequently to
accommodate the pressing demands from
developers~\cite{ecmas262-spec-repo}. An official conformance test
suite exists for \js~\cite{tc39-github}, but, naturally, many test
scenarios are not covered in the suite. In addition, we noticed that a
significant fraction (5 to 15\%) of the tests fail regularly in the
most popular engines, reflecting the struggle of developers in keeping
up with the pace of spec evolution (see Table~\ref{tab:test262}).

%% WHAT WE DID
This work, which is empirical in nature, reports on a study to evaluate the importance of diversity
to find bugs in JavaScript engines; it covers two complementary
diversity-aware testing techniques.

%\vspace{-1ex}
%noitemsep,
\begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
\item \emph{Test transplantation} leverages diversity of test
  cases. This technique evaluates the effect of running test files
  written for a given engine in other engines. The intuition is that
  developers design test cases with different objectives in mind. As
  such, replaying these tests in different engines could reveal
  unanticipated problems.

\item \emph{Cross-engine differential testing} leverages diversity of
  engine implementations. This technique fuzzes existing test
  inputs~\cite{fuzz-testing-history} and then compares the output
  produced by different engines.\Comment{ using a differential
    oracle.} The intuition is that interesting inputs can be created
  from existing inputs and multiple engines can be used to address the
  lack of oracles.
\end{itemize}

The study measures the ability of these techniques in finding bugs and
the impact of false positives on their practicality.

%One of
%various causes of output discrepancy is a bug.

%% It automates test generation in scenarios where multiple
%% implementations of a system exist. DT leverages diversity across
%% system's implementations to detect anomalous behavior.
\emph{Related Ideas.}~The idea of test set diversity dates back to the
eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. In contrast
to prior work on this topic, this paper explores diversity of
implementations and diversity of sources of test cases as opposed to
diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
elaborates related work on this topic. Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files against different configurations of a
given build of their \smonkey\ engine (\eg{}, trying to enable or not
eager JIT compilation\footnote{These files are created with the
  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
is that it can be fully automated---as only one engine is used, the
outcomes of the test in both configurations are expected to be
identical. The Mozilla team uses this approach since 2002; they have
been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). To sum up, variations of these ideas have
been explored before in different contexts.  The goal of the paper is
to assess the ability of the techniques aforementioned in finding bugs
on \javascript\ engines.

%% This paper evaluates the benefits of
%% test case diversity and engine diversity in finding bugs on
%% \javascript\ engines.

%% Recently, Patra and
%% Pradel~\cite{patra2016learning} proposed a language-agnostic fuzzer to
%% find cross-browser HTML+JS discrepancies. The main difference of our
%% work to theirs is in goal; our goal is to evaluate ability and cost of
%% simple diversity-aware approaches to find bugs in \js\ engines.

%% Their main contribution was
%% analytical whereas our main contribution is empirical--

\begin{figure}[t]
%  \vspace{-2ex}  
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
    \includegraphics[trim=0 190 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
    \includegraphics[trim=0 180 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}        
  }
  \caption{\label{fig:summary}Summary of bug reports.}
  \vspace{-3ex}
\end{figure}

\sloppy \emph{Results.}~We considered the following engines--\chakra{}
(Microsoft), JavaScriptCore (Apple), \veight{} (Google), and
\smonkey{} (Mozilla). Figure~\ref{fig:summary} shows the breakdown of
bug reports per engine (\ref{fig:stacked-engine}) and per technique
(\ref{fig:stacked-technique}). Each stacked bar breaks down the bugs
per status (\eg{}, ``1-New''). The prefix number indicates the
ordering that status labels are assigned. Several of these
reports have the label ``3-Fixed'', indicating that bug fixes have
been incorporated into the code already. Note that most of these bugs
affected two engines--\chakra{} and JavaScriptCore (\jsc{}).  We
reported \noBugsBugsReportedGoogle{} bugs in \veight{}
(\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
Furthermore, our results show that both techniques revealed several
bugs, most of which confirmed by developers. Test transplantation
revealed \noBugsTransplantation{} bugs (of which,
\noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
indicate that both techniques were successful at finding bugs. The
number of bug reports were similar, if we consider only those
confirmed or fixed. Most bugs we found are of moderate severity.

%% Considering cost per bug found, we found that test
%% transplantation, compared to differential testing, demanded less
%% effort from the developers who inspected the alarms.

%% All in all, these simple techniques
%% seem promising to improve reliability of engines that continuously
%% evolve with their specifications.

\emph{Key Findings.}~The list of findings of this work includes--1)
Not only multiple different implementations can be leveraged in
differential testing, but differences in test suites can also be
important. 2) Even for problems with fairly clear specifications, as
in \javascript{}, there is likely to be (a lot of) variation between
different implementations. 3) Differential testing is feasible on
real, complex, widely used pieces of
software. Section~\ref{sec:lessons} expands and elaborates key
findings and lessons learned.

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is empirical: 
we provide a comprehensive study analyzing the effectiveness of diversity-aware
techniques to find functional bugs in popular \javascript\ engines.
Additional contributions are:
1)~A number of bugs found and fixed. 
We reported a total of \totalBugsReported{} bugs. 
Of these, \totalBugsConfirmed{} bugs were confirmed and \totalBugsFixed{} bugs were fixed. 
2)~An infrastructure for diversity-aware testing.
The scripts to run the experiments will be available upon request. 
The data is publicly available \dataRepo{}.

\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
that exploring diversity should be encouraged to find functional bugs
in JavaScript engines.

\section{JavaScript}
\label{sec:es6-design}
\label{sec:imp-dep-behavior}

JavaScript engines are virtual machines that parse source code,
compile it in bytecodes, and run these bytecodes. These engines
implement some version of the ECMAScript (\es{}), which emerged with
the goal to standardize variants of the language, such as Netscape's
JavaScript and Microsoft's JScript\footnote{The name JavaScript still
  prevails today, certainly for historical reasons.}. The \es{}
specification is regulated by Ecma International~\cite{es6-website}
under the TC39~\cite{tc39-github} technical committee.  Every year, a
new version of the \es{} specification is produced with new features
and minor fixes. The canonical spec today is
ES6~\cite{ecmas262-spec-repo,ecmas262-spec}.

%% In the following, we briefly describe different sources of
%% discrepancies that can emerge across different engine implementations
%% as results of the active changes in the \es{} specification.
%% .........
%% A compatibility table relating features and supporting engines is
%% publicly available~\cite{kangax}.

The specification of JavaScript is incomplete for different
reasons. Certain parts of the specification are undefined; it is
responsibility of engineers to decide how to implement these
functionalities. The JavaScript spec uses the label
``implementation-dependent'' to indicate these cases, where behavior
may differ from engine to engine. One reason this flexibility in the
spec exists is to enable compiler optimizations. For example, the
\js\ \mcodeid{for-in} loop construct does not clearly specify the
iteration order of
elements~\cite{so-forin-undefined,javascript-in-chrome} and different
engines capitalize on that for loop
optimizations~\cite{for-in-undefined}.  As another example, the
specification states that if the \mcodeid{Number.toPrecision()}
function is called with multiple arguments then the floating-point
approximation is
implementation-dependent~\cite{es6-toPrecision}. Various other cases
like these exist in the specification. Given the speed the
specification changes and the complexity of the language some features
are not fully implemented as can be observed by the Kangax
compatibility table~\cite{kangax}.  It is also worth noting that, as
in other languages, some elements in JS have non-deterministic
behavior (\eg{}, \mcodeid{Math.random} and \mcodeid{Date}). A test
that make decisions based on these elements could, in principle,
produce different outcomes on different runs. Carefully-written test
cases should not manifest this kind of flaky behavior.  As previously
mentioned, all those aspects make testing \js\ engines challenging.

%\subsection{Randomness}

%\subsection{\Fix{Other}}

%% 1) The stack depth in JS is often close to the real (native) C stack
%% depth, nevertheless observable by JS through recursion. This causes
%% differential behavior even on the same engine when JITs are enabled or
%% disabled, as the stack frame sizes vary. LangFuzz in particular
%% produces a lot of recursions and hits these problems even more often
%% than jsfunfuzz.\Mar{ask C. Holler. it is unclear to me how the output
%%   could be different.}

%% \section{Objects of Study}
%% This section discusses the objects we used in our study.

\section{Engines Studied}
\label{sec:methodology}
\label{sec:methodology:engines}~We selected 
JS engines according to the following criteria: 1) Released latest
version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
and 3) Uses a public issue tracker. We looked for highly-maintained
(as per the first criterion) and popular (as per the second criterion)
engines. As we wanted to report bugs, we also looked for project with
public issue trackers. Table~\ref{tab:engines} lists the engines we
analyzed. It is worth noting that we used Google Chrome Lab's JSVU
tool~\cite{jsvu} to automatically install and configure versions of
different JS engines in our host environment. This is important as we
aim to use the most recent stable versions of each engine as to avoid
reporting old and already-fixed bugs to developers.

%% Table~\ref{tab:engines} shows the engines we selected in this
%% study. We made an exception to the second criterion with
%% XS~\cite{xs2018repo}. As the project is young, created in Oct 2017, we
%% thought there was insufficient time to obtain 1K stars for XS. We
%% still considered this project as it seems to be attracting interest
%% from the community\Fix{is this true?}

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:engines}Engines selected.}
  \begin{tabular}{cccrr}
    \toprule
    Team & Name & URL & \# Stars  & DOB \\
    \midrule
    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} &
    \multicolumn{1}{c}{3300+} & Jun 2001\\
    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008\\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009\\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} &
    \multicolumn{1}{c}{1100+} & Mar 1996\\
   \bottomrule     
  \end{tabular}
\end{table}

\section{Mined JS Files}
\label{sec:seeds}
A good test set is critical for finding bugs with the techniques used
in this paper. For that reason, we looked for \js\ files from various
sources: 1) test files from the Test262~\cite{tc39-github} conformance
suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
from the test suite of the selected engines (see
Section~\ref{sec:methodology:engines}); these files are accessible
from the engine's official repositories, 3) test files from the suites
of public engines, and 4) test files mined from issue trackers of
these engines.

%% accessible from GitHub using the GitHub REST
%% API~\cite{github-rest-api}.

Table~\ref{tab:test-suites} shows the breakdown of tests per
engine. Column ``full'' shows the number of test cases associated with
each engine. Column ``pass-in-par.''  shows the number of test cases
that pass in their parent engine. We discarded tests that fail in
their parent engine as we could not reliably indicate the reason for
the failure, so we assumed the test could be broken. We removed \testsThatFail{}
test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc{} and 
\testsThatFailSM{} tests from \smonkey. Column ``type-in-all'' 
shows the number of test cases whose executions do not throw 
dynamic type errors in any of the engines because of an undefined variable or property. 
These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc{}'s
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. For the evaluation of test transplantation, we used
the \totalTestFilesForTestTransplantation{} tests included in the
dashed rectangle under column ``type-in-all'', \ie{}, all tests under
that column but the Test262 tests. We did not consider tests from the
conformance suite as they are more likely to indicate missing features
as opposed to bugs. In addition, engine developers have access to
these test and are encouraged to run them. Finally, column
``no-fail-in-all'' shows the tests for which all engines pass. Note
that the set of tests in this column is a subset of the
``type-in-all'' test set. This test set is used in the evaluation of
differential testing as fuzzing seeds. The guarantee that they pass in
all engines assures that, if discrepancies occur, they are related to
the changes in the input as opposed to the original cause of failure.

\newcommand\marktopleft[1]{%
    \tikz[overlay,remember picture] 
        \node (marker-#1-a) at (0,2ex) {};%
}
\newcommand\markbottomright[1]{%
    \tikz[overlay,remember picture] 
        \node (marker-#1-b) at (0,0) {};%
    \tikz[overlay,remember picture,thick,dashed,inner sep=2pt]
        \node[draw,rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
}

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' (resp., ``no-fail-in-all'')
    shows the tests used for test transplantation (resp., cross-engine
    differential testing).}  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
    \midrule
    \jsc{} & \cite{webkit} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
    \veight{} & \cite{v8} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
    \midrule
    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\ 
    \jerry{} & \cite{jerryscript} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule 
  \end{tabular}
\end{table}

%% The main source of test
%% cases is the official Test262~\cite{tc39-github} conformance test
%% suite for the ECMA262 specification~\cite{ecmas262-spec}.\Comment{
%%   This test suite contains 87\% of all the tests we used.} We also
%% considered test suites of three of the four engines mentioned in
%% Section~\ref{sec:methodology:engines} and four other engines. Overall,
%% we selected a total of \totfiles{} JS
%% files.

\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
depend on external libraries, which not all selected engines
support. We decided to discard those. For example, many tests we found
required a Node.js runtime~\cite{node} for execution. Also, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects. 
Finally, note that the number of tests in
\veight\ is low; that happens because \veight{} uses many tests from
Mozilla and \jsc{}; we discarded those to avoid repetition and to give
credit where it is due. \lbrack{}Test Harness\rbrack{}~It is also
worth mentioning that some engines use a custom shell to run tests,
including a harness with specific assertions.  For that, we needed to
make minor changes in the testing infrastructure to be able to run the
tests uniformly across all engines. More precisely, we needed to mock
non-portable harness functions, which are only available in certain
engines.

\subsection{Mining Tests from Issue Trackers}

\sloppy{}We observed that issue trackers are an important source of
test data and should not be ignored. Analyzing a sample of issues, we
observed that developers either 1) add test cases as attachments of
issues or 2) embed test cases within the textual description of an
issue. The test cases in attachments are longer compared to the test
cases embedded in issue descriptions whereas the latter are more
common. Consequently, we thought we should handle both
cases.

% (\jsc{}=147, \veight{}=370, and \smonkey{}=110).
% (\jsc{}=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
To obtain test files included as attachments, we wrote a crawler to
visit the issue trackers of all engines listed in
Table~\ref{tab:engines} and we were able to retrieve a total of
\filesAttached{} files.  To mine tests from the textual descriptions we
proceeded as follows. First, we broke the text describing the issue in
paragraphs and used a binary classifier to label each paragraph as
``code'' or ``not code'' (\ie{}, natural language). Then, based on
that information, we merged consecutive paragraphs labeled as ``code''
and used a \js\ parser to check well-formedness of the retrieved code
fragment. Using that method we were able to retrieve a total of
\filesMining{} files. All those files were included in
Table~\ref{tab:test-suites}.

For the classification of ``code'' vs. ``not code'', we used a
pipeline of two Neural Networks (NN), a popular design for solving NLP
classification problems~\cite{kusner2015word}. The first net in the
pipeline takes as input an arbitrary sentence and produces on output a
characterization vector for that sentence. The second net in the
pipeline takes that vector on input and produces a yes/no answer,
determining whether or not the input sentence was code.  During the
training phase, the second neural net in the pipeline takes
additionally on input the value for the class attribute for the sample;
in this case, ``code'' or ``not code''. More in detail, for the first
net, we used word2vec~\cite{mikolov2013distributed}, a popular NLP
technique to produce word embeddings. A word embedding is a mapping of
words to vectors of real numbers. For the second net, we used a
multi-layer perceptron~\cite{Rumelhart:1986:LIR:104279.104293} to
infer the probability of the input belonging or not to the class. The
classifier labels the input input as code if the predicted probability
of the input being code is 0.7 or higher. We used a corpus with 25K
samples of English paragraphs and 25K snippets of \js{} code to train
and test the classifier and obtained an accuracy of 98\%. This
classifier is publicly available from our website as a separate
component.

%% With that mapping it is
%% possible to measure distance between two sentences as the distance
%% between the vectors characterizing them. Consequently, one can
%% measure, for example, the minimum distance between a sentence in
%% English and a sentence in a \js\ embedding, built with word2vec using
%% a corpus of \js\ sentences. \Mar{Please confirm if this is the idea!
%%   If yes, shouldn't just one corpus (e.g., the JS corpus) be enough to
%%   solve the problem? Are there two separate embeddings (one for
%%   English and one for JS)? If not, how they are combined? What about
%%   the classification scheme?  It needs to answer yes/no (not a
%%   distance).}

%% For space, we summarize the solution that worked the best in
%% the following. The classifier that performed best for this case uses a
%% standard Embeddings NLP technique~\Fix{cite}\Mar{needs to explain what
%%   this ``Embeddings'' thing does at a high-level. Also, if this stuff
%%   exists why we did not find a solution off-the-shelf?}  that builds
%% on a neural net~\Fix{cite} to keep a dictionary of words and the
%% similarity distance among them\Mar{but we are talking about
%%   sentences. how does it go from words to sentences? Note that many
%%   words from the ``code'' vocabulary are from English!}. In more
%% detail, the classification model uses a Convolutional Neural
%% Network~\Fix{cite} classifier with two layers\Mar{why two? is there a
%%   meaning for each layer?} and has been trained and evaluated using a
%% dataset with 25K samples of English paragraphs and 25K snippets of
%% \js{}. We ran a standard \Fix{X}-repeated 10-fold cross validation to
%% evaluate the model and obtained a predicted accuracy of
%% \Fix{98\%}. This classifier is publicly available from our website as
%% a separate component.

%% N\'os mineramos as issues em bug trackers dos engines javascript mais conhecidos. 
%% Foi necessario capturar tanto os arquivos javascript anexados quanto os codigos escritos nos reports.
%% Para obter o codigo extraido dos reports, foi criado um modelo de aprendizagem para reconhecer
%% se um bloco de texto eh um bloco de codigo.

%% Motivacao:
%% Utilizamos a tecnica de Embeddings que eh reconhecida pela comunidade pelo seu uso em PLN (Processing Language Natural),
%% onde atraves de uma rede neural, consegue-se montar um dicionario de palavras com a distancia 
%% de similaridade entre elas.
%% Para treinamenteo, foi utilizado uma rede neural simples CNN (Convolutional Neural network) com apenas 2 camadas, uma de entrada e outra de saida.
%% Utilizando as variaveis \Fix{XYZ} e as funcoes \Fix{XYZ}. Obtivemos 98\% de acuracia em nosso treinamento.
%% (melhorar definicao do modelo)

%% Inputs:
%% Para nosso modelo de dados, foi necessario gerar um arquivo CSV com cerca de 50K de dados extraidos
%% de arquivos javascript (nossas seeds) e de linguagem natural, utilizamos 25K para cada classe.
%% Os rotulos das classes sao definidas em 0 (is not code) ou 1 (is code).

%% Com isso, extraimos cerca de \Fix{X} codigo e apos realizar o parser para validar o arquivo, obtivemos um total de \Fix{X} novas seeds.

%% \Fix{...elaborate...}

%% \Fix{revise this}
%% For example to run the \jerry{} tests it was necessary 
%% use the unit-test package to run it, but with our changes we added the assertion
%% does not have an assertion in the test file
%% \Fix{add code to explain}

\begin{figure}[t]
  \centering
  \includegraphics[trim=0 350 0 0,clip,width=1.0\textwidth]{diff-testing-runtimes}
  \vspace{-5ex}  
  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
  \vspace{-2ex}
\end{figure}

\section{Cross-Engine Differential Testing}
\label{sec:design}

This section describes the infrastructure we used for cross-engine
differential testing. Figure~\ref{fig:workflow} illustrates the
workflow of the approach. It takes on input a list of JS files and
generates warnings on output. Numbered boxes in the figure denote the
data processors and arrowed lines denote data flows. The cycle icons
indicate repetition--the leftmost icon indicates that each file in the
input list will be analyzed in separate whereas the rightmost icon
shows that a single file will be fuzzed multiple times.

The bug-finding process works as follows. For a given test input, the
toolchain produces new inputs using some off-the-shelf input fuzzer
(step 1).  (Section~\ref{sec:objects:fuzzers} describes the fuzzers we
selected.)  Then, the oracle checks whether or not the output produced
for the fuzzed file is consistent across all engines (step 2). In case
the test passes in all engines or fails in all engines (\ie{}, the
output is consistent), the infrastructure ignores the
input. Otherwise, it considers the input as potentially
fault-revealing; hence, interesting for human inspection. Finally, to
facilitate the human inspection process, the infrastructure
prioritizes warnings and clusters them in groups (step 3). We describe
these features in Sections~\ref{sec:prioritization} and
\ref{sec:clusterization}. Note that a number of reasons exist, other
than a bug, to explain discrepancy (see
Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}) and there is no clear automatic approach
to precisely distinguish false and true positives. As such, a human
needs to inspect the warning to classify the issue. As mentioned
earlier, this justifies why differential testing is challenging to
automate at the functional level.

>>>>

\chapter{Related Work}
\label{sec:related}
\section{Diversity in Testing}
\label{sec:related:diversity-testing}
The idea of test set diversity dates back to the
eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. The
assumption behind test set diversity is that faults often spread
contiguously in the input domain. Consequently, it should be
beneficial to partition the input domain and explore it more evenly as
to find bugs faster. Later in the nineties, Chen and
Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
the continuity assumption. They found that faults, most often,
manifest themselves in regular patterns across the input
domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
observations led researchers to investigate generalizations of the
approach to non-numerical data types and strategies to explore the
input (or output) space to solve different problems in Software
Engineering (\eg{}, test input generation and test
selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
study explores diversity of sources of test cases and diversity of
engine implementations. We remain to investigate the diversity of test
cases themselves. In principle, that could help reduce the number of
alarms to inspect, for example.

\section{Differential Testing}
Several different applications of differential testing have been
proposed in recent years. Chen and
colleagues~\cite{Chen:2018:RDT:3180155.3180226} recently proposed a
technique to generate X.509 certificates based on Request For
Proposals (RFC) as specification with the goal of detecting bugs in
different SSL/TLS implementations. Those bugs can compromise security
of servers which rely on these certificates to properly authenticate
the parties involved in a communication session. Lidbury and
colleagues~\cite{Lidbury:2015:MCF:2737924.2737986} and Donaldson and
colleagues~\cite{Donaldson:2017:ATG:3152284.3133917} have been
focusing on finding bugs in programs for graphic cards (\eg{},
OpenCL). These programs use the Single-Instruction Multiple-Data
(SIMD) programming abstraction and typically run on GPUs.  Perhaps the
application of differential testing that received most attention to
date was compiler testing. In 1972, Purdom~\cite{Purdom1972} proposed
the use of a generator of sentences from grammars to test correctness
of automatically generated parsers. After that, significant progress
has been made. Lammel and Shulte proposed Geno to cross-check XPath
implementations using grammar-based testing with controllable
combinatorial coverage~\cite{10.1007/11754008_2}. Yang and
colleagues~\cite{Yang:2011:FUB:1993498.1993532} proposed CSmith to
randomly create C programs from a grammar, for a subset of C, and then
check the output of these programs in different compilers (\eg{}, GCC
and LLVM). Le and colleagues~\cite{Le:2014:CVV:2594291.2594334}
proposed ``equivalence modulo inputs'', which creates variants of
program which should have equivalent behavior compared to the
original, but for which the compiler manifests
discrepancy. Differential testing has also been applied to test
refactoring engines~\cite{Daniel:2007:ATR:1287624.1287651}, to test
symbolic engine implementations~\cite{Kapus:2017:ATS:3155562.3155636},
to test disassemblers and binary
lifters~\cite{Paleari:2010:NDD:1831708.1831741,Kim:2017:TIR:3155562.3155609},
and very recently to test JavaScript
debuggers~\cite{DBLP:conf/sigsoft/LehmannP18}. All in all, it has
shown to be flexible and effective for a wide range of
applications. Surprisingly, not much work has been done on
differential testing of \js\ engines. Mozilla uses differential
testing to look for discrepancies across different configurations of
the same version of its \smonkey\ engine (using the ``compare\_jit''
flag of jsfunfuzz~\cite{jsfunfuzz}) whereas we focus on discrepancy
across engines. \citeonline{patra2016learning} evaluated their language-agnostic
fuzzing strategy using differential testing. Their focuses on finding
differential bugs across multiple
browsers. As such they specialized their
fuzzer to HTML and JS (see Section~\ref{sec:testing-js-engines}).
\Igor{In \citeonline{Chen-etal-pldi16} is presented the \textit{classfuzz}, a tool
that uses coverage-directed fuzzing technique to improving the generation
of valid mutants on different JVM implementations. In this case, their focuses
is the Java environment and evaluate their technique with another coverage-directed
fuzzing. In contrast to \citeonline{patra2016learning} and \citeonline{Chen-etal-pldi16}, we did not propose new techniques; our
contribution was empirical.
}

\section{Testing \js\ Programs}
Patra and colleagues~\cite{Patra:2018:CFU:3180155.3180184} proposed a
lightweight approach to detect conflicts in \js\ libraries that occur
when names introduced by different libraries collide. This problem was
found to be common as the design of \js\ allows for overlaps in
namespaces. A similar problem has been investigated by Nguyen and
colleagues~\cite{nguyen-etal-icse2014} and Eshkevari and
colleagues~\cite{eshkevari-etal-icpc2014} in the context of PHP
programs, which are popular in the context of Content Management
Systems as WordPress. The focus of this work is on testing
\js\ engines as opposed to \js\ programs. Our goal is therefore
orthogonal to theirs.

\section{Testing \js{} Engines}
\label{sec:testing-js-engines}
The closest work to ours was done by \citeonline{patra2016learning}. Their work proposes a
language-agnostic fuzzer to find cross-browser HTML+JS
discrepancies.%\Comment{ They applied the proposed fuzzer to find bugs in JS engines and Web Assembly engines.}
The sensible parts of the infrastructure they
built are the checks of input validity (as to reduce waste/cost) and
output correctness (as to reduce FP). Patra and Pradel
work is complementary to ours--in principle, we could use their fuzzer
in our evaluation. The main difference of our work to theirs is in
goal--we aim at assessing reliability of \js\ engines and find bugs on
them using simple approaches whereas they aim at proposing a new
technique.
